A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2017-11-30 analysis/paper/paper.Rmd
clean up the reference list and citations

This is a useful definition because it emphasizes data as digital manifestations, and so suitable for transmission, storage and retrieval using the internet. Physical objects (such as samples, collections, hard copies of notes, etc.) are data also, but they are out of scope of this discussion because of the different challenges and requirements for access, archiving, and so on. The categories shown in Table \@ref(tab:types-of-data) are useful as a rough guide to what data can be, although this table is not comprehensive, and does not represent the full diversity of data used by archaeologists. Ultimately, data are whatever the community decides, as the The National Science Foundation notes in their commentary on Data Management Plans: "What constitutes such data will be determined by the community of interest through the process of peer review and program management. This may include, but is not limited to: data, publications, samples, physical collections, software and models." These definitions in policy are consistent with the relational account of data in philosophy of science scholarship, which holds that what data are is dependent on who uses it, how and for what purpose (Leonelli 2015; Daston and Galison 1992). How can these definitions and philosophical discussions inform our practice? They tell us that what counts as data is emergent from our professional interactions. Data are the materials we request when we do peer review of manuscripts and grant proposals, or when we make an informal request for more information by email. They are not exclusively objective archaeometric records, but include interpretive and derivative results. In short, data are anything another person needs to understand our work better.

@@

Stodden (2010) surveyed registrants at a top machine learning conference (the Neural Information Processing Systems (NIPS) conference) to identify the factors that affect researchers’ decisions to reveal data (Table \@ref(tab:costsbenefits)). Stodden found that communitarian factors influence scientists to share their data, but private incentives determine when scientists choose not to share their code and data. In the top three reasons not to share, we see a lack of incentives to invest time in data sharing (however, there are many other time-consuming tasks in research, and they get done because clear reward structures are in place); a lack of faith in data citation (which we hope this paper will help with); and a lack of an efficient copyright process. Stodden’s (2009a, b) ‘Reproducible Research Standard’, summarized in Table \@ref(tab:stodden-rrs), is a convenient and robust copyright schema that is in wide use for many typical research projects.

@@

We can get some insights into the impact of repository data by querying the Crossref (2017) Events Data service, a freely accessible DOI citation dataset produced by periodic scanning of a variety of online sources. Crossref is an official DOI registration agency, focused on issuing DOIs for scholarly materials such as journal articles, books, ebooks, etc. Another source for data citation data is Thomson Reuters' Data Citation Index (Pavlech 2016), but this resource is not free, and we did not have access to a subscription. Of the `r prettyNum(length(dc_arch$doi), big.mark = ",")` DOIs in our sample, we found a total of `r nrow(events_df)` citations of `r length(unique(events_df$obj_id))` unique DOIs in the Crossref events data. The majority of these citations were found on Wikipedia \@ref(fig:citation-plot), followed by other data repositories (i.e. cross-citations from one data set to another in the same repository). The largest source of citations is the Zenodo repository, followed by articles in the journal _Medieval Archaeology_, which appear here because volumes 1-50 are hosted by the Archaeology Data Service. According to the Crossref data, citation of archaeological data in repositories is a recent phenomena, with the majority in our sample occurring over the last twelve months. We found only one example of a dataset DOI cited in a journal article (McCoy and Codlin 2016). This may be an underestimate, given Huggett's (2017) finding that 56 of 476 archaeology data sources in Thomson Reuters' Data Citation Index have citations in Web of Science databases. However, Huggett notes that the Thomson Reuters citation data is unreliable, for example, with incomplete citations, and citations that pre-date the cited dataset. Huggett also shows an example of archaeologists citing datasets but omitting the DOI (e.g. Nugent and  Williams 2012), so the citation is not captured by services such as Crossref or Thomson Reuters. These malformed citations add to the difficulty of accurately measuring data citation in archaeology.

@@

In the pilot studies reported above we see three common approaches to sharing data: sending files privately by email, following a personal request; including data as supplementary files submitted for publication with a journal article; and sharing data by depositing files in a trustworthy, public, DOI-issuing repository. The third method, via a public repository, is by far the most widely recommended method both specifically by archaeologists (Kintigh 2006; Kansa et al. 2011; Kansa and Kansa 2013), and in other sciences (cf. Cranston et al. 2014; Penev et al. 2017; Mounce 2014; Thessen & Patterson 2011; Whitlock 2011). List of trustworthy repositories are maintained by the editors of the journal _Scientific Data_ (n.d) and <http://www.re3data.org>, a global registry of research data repositories (Pampel et al. 2013). University librarians are another resource for advice on choosing repositories and preparing data for sharing. There are many guidelines and conventions from other disciplines that are relevant to sharing archaeological data (ICPSR 2012; Strasser et al. 2012; Wilkinson et al. 2016). Table \@ref(tab:desirable) summarizes some of these, and recommendations specifically written for archaeologists can be found in UK Archaeology Data Service (n.d.), ARCHES project. (n.d.). Many of these guidelines may create new technical and practical challenges to archaeologists who are not accustomed to sharing data, and many not want to dedicate resources to sharing data. However, we should not let the perfect be the enemy of the good. In our own work we try to follow these guidelines with no dedicated resources for data sharing, and with an incomplete knowledge of some of the technical details of repository operations. While we recognize that our data sharing practices fall short of all the guidelines, we still see value in sharing data imperfectly, rather than not at all.

@@

“The data underpinning the analysis reported in this paper were deposited in the Open Science Framework Repository at http://doi.org/10.17605/OSF.IO/32A87 (Marwick 2017).

@@

```{r desirable}
tbl <- readr::read_csv("../figures/tbl_rules_of_data_sharing.csv")
knitr::kable(tbl, caption = "Nine key things to do with your data, from Hart et al. (2016) ")
```

@@

# References

Alsheikh-Ali AA, Qureshi W, Al-Mallah MH, Ioannidis JPA (2011) Public Availability of Published Research Data in High-Impact Journals. PLOS ONE 6(9): e24357. https://doi.org/10.1371/journal.pone.0024357

American Psychological Association. (2001). Ethical standards for the reporting and publishing of scientiﬁc information. In Publication manual of the American Psychological Association (5th ed., pp. 387–396). Washington, DC

ARCHES project. (n.d.). The Standard and Guide to Best Practice in Archaeological Archiving in Europe. Retrieved September 7, 2017, from http://archaeologydataservice.ac.uk/arches/Wiki.jsp?page=ARCHES%20Introduction

Bierer, B.E., Crosas, M., Pierce, H.H., 2017. Data Authorship as an Incentive to Data Sharing, New England Journal of Medicine. 376(17):1684-1687

Borgman, C. L. (2015). Big data, little data, no data: Scholarship in the networked world. MIT press.

Borgman, C. L. (2012). The conundrum of sharing research data. Journal of the American Society for Information Science and Technology, 63(6), 1059–1078. doi:10.1002/asi.22634

Chambers, C. (2017). The seven deadly sins of psychology: A manifesto for reforming the culture of scientific practice. Princeton, NJ: Princeton University Press.

Clarke, Mary. (2015). The Digital Dilemma: Preservation and the Digital. Archaeological Record. Advances in Archaeological Practice. 3(4): 313-330.

Crossref (2017). Event Data User Guide, Version 1.0.0 - Beta. Retrieved November 7, 2017, from https://www.eventdata.crossref.org/guide/

Daston, Lorraine, Galison Peter. (1992) The Image of Objectivity. Representations. 40:81–128.

Dorch, B. F., Drachen, T. M., & Ellegaard, O. (2015). The data sharing advantage in astrophysics. Proceedings of the International Astronomical Union, 11(A29A), 172-175.

Duke, C. S., & Porter, J. H. (2013). The Ethics of Data Sharing and Reuse in Biology. BioScience, 63(6), 483–489. https://doi.org/10.1525/bio.2013.63.6.10

Editors, (2013). Guide for Authors. Journal of Archaeological Science. Retrieved September 7, 2017, from https://web.archive.org/web/20130125222940/https://www.elsevier.com/journals/journal-of-archaeological-science/0305-4403/guide-for-authors

Ellison, L. A. (2012). Just 20 days left!! Upload your archaeological information FREE to tDAR!! | The Digital Archaeological Record. Retrieved September 7, 2017, from https://www.tdar.org/news/2012/12/just-20-days-left-upload-your-archaeological-information-free-to-tdar/

Eglen, S. J., Marwick, B., Halchenko, Y. O., Hanke, M., Sufi, S., Gleeson, P.,  Poline, J.-B. (2017). Toward standard practices for sharing computer code and programs in neuroscience. Nature Neuroscience, 20(6), 770–773. https://doi.org/10.1038/nn.4550

Fienberg, S. E., Martin, M. E., & Straf, M. L. (1985). Sharing research data. National Academy Press, Washington DC.

Giofrè, D., Cumming, G., Fresc, L., Boedker, I., & Tressoldi, P. (2017). The influence of journal submission guidelines on authors’ reporting of statistics and use of open research practices. PLoS ONE, 12(4). https://doi.org/10.1371/journal.pone.0175583

Gleditsch, N. P., Metelits, C., & Strand, H. (2003). Posting your data: will you be scooped or will you be famous. International Studies Perspectives, 4(1), 89-97.

Hagstrom, W O (1982). Gift Giving as an Organising Principle in Science In: Barnes, B and Edge, D eds.  Science in Context: Readings in the Sociology of Science. Milton Keynes, United Kingdom: The Open University Press, pp. 21–34.

Hart, E. M., Barmby, P., LeBauer, D., Michonneau, F., Mount, S., Mulrooney, P., Hollister, J. W. (2016). Ten Simple Rules for Digital Data Storage. PLOS Computational Biology, 12(10), e1005097. https://doi.org/10.1371/journal.pcbi.1005097

Henneken, E. A., & Accomazzi, A. (2011). Linking to data-effect on citation rates in astronomy. arXiv preprint, arXiv:1111.3618.

Huggett, J. (2017, May 23). Citing Data Reuse. Retrieved September 7, 2017, from https://introspectivedigitalarchaeology.wordpress.com/2017/05/23/citing-data-reuse/

Hymes, D. (1972). 1974. Reinventing anthropology. New York: Pantheon

Inter-university Consortium for Political and Social Research (ICPSR). (2012). Guide to Social Science Data Preparation and Archiving: Best Practice Throughout the Data Life Cycle (5th ed.). Ann Arbor, MI

Kidwell, M. C., Lazarević, L. B., Baranski, E., Hardwicke, T. E., Piechowski, S., Falkenberg, L. S., & Errington, T. M. (2016). Badges to acknowledge open practices: A simple, low-cost, effective method for increasing transparency. PLoS Biol, 14(5), e1002456.

Keers, G., van der Reijden, H., and van Rossum, H. 2011. Planning Archaeology: A Synthesis of the Thematic Sub-reports. Amsterdam: Rigo.

Kratz JE, Strasser C (2015) Researcher Perspectives on Publication and Peer Review of Data. PLOS ONE 10(2): e0117619. doi: 10.1371/journal.pone.0117619

Kratz J and Strasser C. Data publication consensus and controversies [version 1; referees: 1 approved with reservations]. F1000Research 2014, 3:94
(doi: 10.12688/f1000research.3979.1)

Kyzas PA, Loizou KT, and Ioannidis JP. (2005) Selective reporting biases in cancer prognostic factor studies. Journal of the National Cancer Institute 97, 1043-1055.

Leonelli, S. (2016). The philosophy of data, In Floridi, L. (Ed.) The Routledge Handbook of Philosophy of Information. Routledge, NY.

Marwick, B. (2017). Computational reproducibility in archaeological research: Basic principles and a case study of their implementation. Journal of Archaeological Method and Theory, 24(2), 424-450.

McCoy, M. D., and M. C. Codlin. (2016). The Influence of Religious Authority in Everyday Life: A Landscape-Scale Study of Domestic Architecture and Religious Law in Ancient Hawai’i. World Archaeology 48 (3):411–30.

McCullough BD, McGeary KA, Harrison TD. (2006) Lessons from the JMCB Archive. Journal of Money, Credit, and Banking 38(4), 1093-1107. doi:10.1353/mcb.2006.0061

McCullough BD and Vinod HD. (2005) Comment: Econometrics and Software. Journal of Economic Perspectives 17(1), 223-224.

McMurry, J. A., Juty, N., Blomberg, N., Burdett, T., Conlin, T., Conte, N., Parkinson, H., Winfree, L., Mungall, C., Haendel, M., H. Parkinson (2017). Identifiers for the 21st century: How to design, provision, and reuse persistent identifiers to maximize utility and impact of life science data. PLOS Biology, 15(6), e2001414. https://doi.org/10.1371/journal.pbio.2001414

Merton, R.K. (1942) "The Normative Structure of Science". In: Merton, R. K., The Sociology of Science: Theoretical and Empirical Investigations, Chicago, IL: University Of Chicago Press.

Moore, R., & Richards, J. (2015). Here Today, Gone Tomorrow: Open Access, Open Data and Digital Preservation. In Andrew T. Wilson, Ben Edwards (eds) Open Source Archaeology: Ethics and Practice. De Gruyter, Netherlands

Nicholas, G. (2014). Indigenous cultural heritage in the age of technological reproducibility: Towards a postcolonial ethic of the public domain. In Coombe, R. J., Wershler, D., & Zeilinger, M. (Eds.) Dynamic fair dealing: creating Canadian culture online. University of Toronto Press. pp. 213-24.

Nichols, D.M., Twidale, M.B., (2017). Metrics for openness, Journal of the Association for Information Science and Technology 68, 1048-1060.

Nicholas, G. P., & Wylie, A. (2012). Do Not Do Unto Others…’: Cultural misrecognition and the harms of appropriation in an open-source world. Appropriating the Past: Philosophical Perspectives on Archaeological Practice, 195-221.

Nicholas, G. P., & Wylie, A. (2009). Archaeological finds: legacies of appropriation, modes of response. The Ethics of Cultural Appropriation, 11-54.

Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J., Yarkoni, T. (2015). Promoting an open research culture: Author guidelines for journals could help to promote transparency, openness, and reproducibility. Science, 348, 1422–5.

Nuijten, M. B., Borghuis, J., Veldkamp, C. L. S., Alvarez, L. D., van Assen, M. A. L. M., & Wicherts, J. M. (2017, July 13). Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psychology. Retrieved September 7, 2017, from psyarxiv.com/sgbta

National Science Board. (2005). Long-lived digital data collections. Retrieved September 7, 2017, from http://www.nsf.gov/pubs/2005/nsb0540/

National Science Foundation. (2010). Data Management & Sharing Frequently Asked Questions (FAQs). Retrieved September 7, 2017, from https://www.nsf.gov/bfa/dias/policy/dmpfaqs.jsp#1

National Science Foundation. (2016). Dissemination and Sharing of Research Results. Retrieved September 7, 2017, from https://www.nsf.gov/bfa/dias/policy/dmp.jsp

Pampel, H., Vierkant, P., Scholze, F., Bertelmann, R., Kindling, M., Klump, J. & Dierolf, U. (2013). Making research data repositories visible: The re3data.org registry. PloS one, 8(11), e78080.

Pavlech, L. L. (2016). Data Citation Index. Journal of the Medical Library Association : JMLA, 104(1), 88–90.

Peng RD, Dominici F, and Zeger SL. (2006) Reproducible Epidemiological Research. American Journal of Epidemology 163, 783-789 doi: 10.1093/aje/kwj093

Penev L, Mietchen D, Chavan V, Hagedorn G, Smith V, Shotton D, Ó Tuama É, Senderov V, Georgiev T, Stoev P, Groom Q, Remsen D, Edmunds S (2017) Strategies and guidelines for scholarly publishing of biodiversity data. Research Ideas and Outcomes 3: e12431. https://doi.org/10.3897/rio.3.e12431

Piwowar HA, Day RS, Fridsma DB (2007) Sharing Detailed Research Data Is Associated with Increased Citation Rate. PLOS ONE 2(3): e308. https://doi.org/10.1371/journal.pone.0000308

Piwowar, H. A., & Vision, T. J. (2013). Data reuse and the open data citation advantage. PeerJ, 1, e175. https://doi.org/10.7717/peerj.175

PLoS Medicine Editorial and Publishing Policies. 13. Sharing of Materials, Methods and Data. PLoS Medicine Editorial and Publishing Policies. Retrieved September 7, 2017, from http://journals.plos.org/plosmedicine/policies.php#sharing.

Reichman, J. H., & Uhlir, P. F. (2003). A contractually reconstructed research commons for scientific data in a highly protectionist intellectual property environment. Law and Contemporary problems, 66(1/2), 315-462.

Reidpath DD, and Allotey PA. Data Sharing in Medical Research: An Empirical Investigation. Bioethics 15(2), 125- 134 (2002). doi: 10.1111/1467-8519.00220

Rowhani-Farid, A., Allen, M., & Barnett, A. G. (2017). What incentives increase data sharing in health and medical research? A systematic review. Research Integrity and Peer Review, 2(1), 4. https://doi.org/10.1186/s41073-017-0028-9

Savage CJ, Vickers AJ (2009) Empirical Study of Data Sharing by Authors Publishing in PLoS Journals. PLoS ONE 4(9): e7078. doi:10.1371/journal.pone.0007078

Sawyer, S. (2008). Data wealth, data poverty, science and cyberinfrastructure 1. Prometheus, 26(4), 355-371.

Scientific Data Editors (n.d) Recommended Data Repositories. Retrieved September 13, 2017, from https://www.nature.com/sdata/policies/repositories

Sears, J.R.L (2011) Data sharing effect on article citation rate in paleoceanography. Presented at Fall Meeting of the American Geophysical Union. Retrieved September 7, 2017, from https://doi.org/10.6084/M9.FIGSHARE.1222998.V1

Spencer, Hilary (2010). Thoughts on the sharing of data and research
materials and the role of journal policies. Retrieved September 7, 2017, from https://web.stanford.edu/~vcs/Nov21/hilary_spencer_rdcscsJan2010.pdf

Strasser, C., Cook, R., Michener, W., & Budden, A. (2012). Primer on Data Management: What you always wanted to know. EScholarship. Retrieved September 7, 2017, from https://doi.org/10.5060/D2251G48

>>>>

This is a useful definition because it emphasizes data as digital manifestations, and so suitable for transmission, storage and retrieval using the internet. Physical objects (such as samples, collections, hard copies of notes, etc.) are data also, but they are out of scope of this discussion because of the different challenges and requirements for access, archiving, and so on. The categories shown in Table \@ref(tab:types-of-data) are useful as a rough guide to what data can be, although this table is not comprehensive, and does not represent the full diversity of data used by archaeologists. Ultimately, data are whatever the community decides, as the The National Science Foundation (2010) notes in their commentary on Data Management Plans: "What constitutes such data will be determined by the community of interest through the process of peer review and program management. This may include, but is not limited to: data, publications, samples, physical collections, software and models." These definitions in policy are consistent with the relational account of data in philosophy of science scholarship, which holds that what data are is dependent on who uses it, how and for what purpose (Leonelli 2015; Daston and Galison 1992). How can these definitions and philosophical discussions inform our practice? They tell us that what counts as data is emergent from our professional interactions. Data are the materials we request when we do peer review of manuscripts and grant proposals, or when we make an informal request for more information by email. They are not exclusively objective archaeometric records, but include interpretive and derivative results. In short, data are anything another person needs to understand our work better.

@@

Stodden (2010) surveyed registrants at a top machine learning conference (the Neural Information Processing Systems (NIPS) conference) to identify the factors that affect researchers’ decisions to reveal data (Table \@ref(tab:sharingbenefits)). Stodden found that communitarian factors influence scientists to share their data, but private incentives determine when scientists choose not to share their code and data. In the top three reasons not to share, we see a lack of incentives to invest time in data sharing (however, there are many other time-consuming tasks in research, and they get done because clear reward structures are in place); a lack of faith in data citation (which we hope this paper will help with); and a lack of an efficient copyright process. Stodden’s (2009a, b) ‘Reproducible Research Standard’, summarized in Table \@ref(tab:stodden-rrs), is a convenient and robust copyright schema that is in wide use for many typical research projects.

@@

We can get some insights into the impact of repository data by querying the Crossref (2017) Events Data service, a freely accessible DOI citation dataset produced by periodic scanning of a variety of online sources. Crossref is an official DOI registration agency, focused on issuing DOIs for scholarly materials such as journal articles, books, ebooks, etc. Another source for data citation data is Thomson Reuters' Data Citation Index (Pavlech 2016), but this resource is not free, and we did not have access to a subscription. Of the `r prettyNum(length(dc_arch$doi), big.mark = ",")` DOIs in our sample, we found a total of `r nrow(events_df)` citations of `r length(unique(events_df$obj_id))` unique DOIs in the Crossref events data. The majority of these citations were found on Wikipedia (Figure \@ref(fig:citation-plot)), followed by other data repositories (i.e. cross-citations from one data set to another in the same repository). The largest source of citations is the Zenodo repository, followed by articles in the journal _Medieval Archaeology_, which appear here because volumes 1-50 are hosted by the Archaeology Data Service. According to the Crossref data, citation of archaeological data in repositories is a recent phenomena, with the majority in our sample occurring over the last twelve months. We found only one example of a dataset DOI cited in a journal article (McCoy and Codlin 2016). This may be an underestimate, given Huggett's (2017) finding that 56 of 476 archaeology data sources in Thomson Reuters' Data Citation Index have citations in Web of Science databases. However, Huggett notes that the Thomson Reuters citation data is unreliable, for example, with incomplete citations, and citations that pre-date the cited dataset. Huggett also shows an example of archaeologists citing datasets but omitting the DOI (e.g. Nugent and  Williams 2012), so the citation is not captured by services such as Crossref or Thomson Reuters. These malformed citations add to the difficulty of accurately measuring data citation in archaeology.

@@

In the pilot studies reported above we see three common approaches to sharing data: sending files privately by email, following a personal request; including data as supplementary files submitted for publication with a journal article; and sharing data by depositing files in a trustworthy, public, DOI-issuing repository. The third method, via a public repository, is by far the most widely recommended method both specifically by archaeologists (Kintigh 2006; Kansa et al. 2011; Kansa and Kansa 2013), and in other sciences (cf. Cranston et al. 2014; Penev et al. 2017; Mounce 2014; Thessen & Patterson 2011; Whitlock 2011). List of trustworthy repositories are maintained by the editors of the journal _Scientific Data_ (n.d) and <http://www.re3data.org>, a global registry of research data repositories (Pampel et al. 2013). University librarians are another resource for advice on choosing repositories and preparing data for sharing. There are many guidelines and conventions from other disciplines that are relevant to sharing archaeological data (ICPSR 2012; Strasser et al. 2012; Wilkinson et al. 2016). Table \@ref(tab:desirable) summarizes some of these, and recommendations specifically written for archaeologists can be found in Archaeology Data Service / Digital Antiquity (2011) and ARCHES project. (n.d.). Many of these guidelines may create new technical and practical challenges to archaeologists who are not accustomed to sharing data, and many not want to dedicate resources to sharing data. However, we should not let the perfect be the enemy of the good. In our own work we try to follow these guidelines with no dedicated resources for data sharing, and with an incomplete knowledge of some of the technical details of repository operations. While we recognize that our data sharing practices fall short of all the guidelines, we still see value in sharing data imperfectly, rather than not at all.

@@

"The data underpinning the analysis reported in this paper were deposited in the Open Science Framework Repository at http://doi.org/10.17605/OSF.IO/32A87 (Marwick 2017)."

@@

```{r desirable}
tbl <- readr::read_csv("../figures/tbl_rules_of_data_sharing.csv")
knitr::kable(tbl, caption = "Nine key things to do before sharing your data, from Hart et al. (2016) and White et al. (2013)")
```

@@

# References Cited

Alsheikh-Ali A.A., Qureshi W., Al-Mallah M.H. and J. Ioannidis
2011. Public Availability of Published Research Data in High-Impact Journals. PLOS ONE 6(9): e24357. DOI:10.1371/journal.pone.0024357, accessed 7 September 2017.
American Psychological Association
2001.	Ethical Standards for the Reporting and Publishing of Scientiﬁc Information. In Publication Manual edited by American Psychological Association, pp. 387–396. Washington, DC
ARCHES project
n.d. The Standard and Guide to Best Practice in Archaeological Archiving in Europe. Electronic document, http://archaeologydataservice.ac.uk/arches/Wiki.jsp?page=ARCHES%20Introduction, accessed on 7 September 2017.
Bogen J, and J. Woodward
1998.	Saving the Phenomena. The Philosophical Review 97(3): 303–352
Borgman, C. L. 
2015.	Big Data, Little Data, No Data: Scholarship in the Networked World. MIT Press, Massachusetts. 
Borgman, C. L. 
2012.	The Conundrum of Sharing Research Data. Journal of the American Society for Information Science and Technology, 63(6), 1059–1078.
Chambers, C. 
2017.	The Seven Deadly Sins of Psychology: A Manifesto for Reforming the Culture of Scientific Practice. Princeton University Press, Princeton, New Jersey. 
Clarke, M.
2015.	The Digital Dilemma: Preservation and the Digital. Archaeological Record. Advances in Archaeological Practice. 3(4): 313-330.
Cranston K, Harmon L. J., O'Leary, M. A. and C. Lisle
2014.	Best Practices for Data Sharing in Phylogenetic Research. PLOS Currents Tree of Life. (blog) 19 Jun 2014, DOI: 10.1371/currents.tol.bf01eff4a6b60ca4825c69293dc59645, accessed 7 September 2017
Crossref 
2017. Event Data User Guide, Version 1.0.0 - Beta. Electronic document, https://www.eventdata.crossref.org/guide/, accessed 7 November  2017.
Daston, L, and P. Galison
1992.	 The Image of Objectivity. Representations. 40:81–128.
Data Citation Synthesis Group
2014.	Joint Declaration of Data Citation Principles. In FORCE11; 2014 edited by Martone M., Electronic document, https://doi.org/10.25490/a97f-egyk, accessed on 7 September 2017. 
Dorch, B. F., Drachen, T. M., and O. Ellegaard
2015.	The Data Sharing Advantage in Astrophysics. Proceedings of the International Astronomical Union, 11(A29A), 172-175.
Duke, C. S., and J. H. Porter
2013.	The Ethics of Data Sharing and Reuse in Biology. BioScience, 63(6), 483–489. 
Editors
2013.	Guide for Authors. Journal of Archaeological Science. Electronic document, https://web.archive.org/web/20130125222940/https://www.elsevier.com/journals/journal-of-archaeological-science/0305-4403/guide-for-authors, accessed 7 September 7, 2017
Ellison, L. A. 
2012.	Just 20 days left!! Upload Your Archaeological Information FREE to tDAR!! | The Digital Archaeological Record (blog). Electronic document https://www.tdar.org/news/2012/12/just-20-days-left-upload-your-archaeological-information-free-to-tdar/, accessed 7 September 2017
Eglen, S. J., Marwick, B., Halchenko, Y. O., Hanke, M., Sufi, S., Gleeson, P., J.-B. Poline
2017.	Toward Standard Practices for Sharing Computer Code and Programs in Neuroscience. Nature Neuroscience, 20(6), 770–773. 
Fienberg, S. E., Martin, M. E., & Straf, M. L. 
1985	Sharing Research Data. National Academy Press, Washington DC.
Floridi, L. 
2011.	The Philosophy of Information. Oxford University Press, London.
Giofrè, D., Cumming, G., Fresc, L., Boedker, I., and P. Tressoldi
2017.	The influence of journal submission guidelines on authors’ reporting of statistics and use of open research practices. PLoS ONE, 12(4). DOI:10.1371/journal.pone.0175583, accessed on 7 September 2017
Gleditsch, N. P., Metelits, C., and H. Strand
2003.	Posting Your Data: Will You be Scooped or will You be Famous. International Studies Perspectives, 4(1), 89-97.
Hacking I.
1992.	The Self-Vindication of the Laboratory Sciences. In Science as Practice and Culture, edited by Andrew Pickering. The University of Chicago Press, pp. 29–64, Chicago, Illinois. 
Hagstrom, W O. 
1982.	Gift Giving as an Organising Principle in Science In Science in Context: Readings in the Sociology of Science edited by B. Barnes and D. Edge, pp. 21–34, The Open University Press, Milton Keynes. 
Harding, A., Harper, B., Stone, D., O’Neill, C., Berger, P., Harris, S., and J. Donatuto
2012.	Conducting Research with Tribal Communities: Sovereignty, Ethics, and Data-Sharing Issues. Environmental Health Perspectives, 120(1), 6.
Hart, E. M., Barmby, P., LeBauer, D., Michonneau, F., Mount, S., Mulrooney, P., and , J. W. Hollister
2016.	Ten Simple Rules for Digital Data Storage. PLOS Computational Biology, 12(10), e1005097. DOI:10.1371/journal.pcbi.1005097, accessed on 7 September 2017
Henneken, E. A., and A. Accomazzi
2011.	Linking to Data-Effect on Citation Rates in Astronomy. Electronic document, https://arxiv.org/abs/1111.3618, accessed 17 September 2017
Huggett, J. 
2017	Citing Data Reuse. Electronic document, https://introspectivedigitalarchaeology.wordpress.com/2017/05/23/citing-data-reuse/, accessed September 7, 2017
Hymes, D. 
1972.	Reinventing Anthropology. Pantheon, New York.
Inter-university Consortium for Political and Social Research
2012.	Guide to Social Science Data Preparation and Archiving: Best Practice Throughout the Data Life Cycle (5th ed.). Institute for Social Research University of Michigan, Ann Arbor, Michigan
Kansa, E. C. and S. W. Kansa
2013.	Open Archaeology: We All Know That a 14 Is a Sheep: Data Publication and Professionalism in Archaeological Communication. Journal of Eastern Mediterranean Archaeology & Heritage Studies, 1(1), 88-97.
Kansa, E. C., S. W. Kansa and E. Watrall, E. (editors)
2011.	Archaeology 2.0: new approaches to communication and collaboration. Cotsen Digital Archaeology Series, University of California, Electronic document, https://escholarship.org/uc/item/1r6137tb, accessed 7 November 2017
Kidwell, M. C., Lazarević, L. B., Baranski, E., Hardwicke, T. E., Piechowski, S., Falkenberg, L. S. and T. M. Errington
2016.	Badges to Acknowledge Open Practices: A Simple, Low-cost, Effective Method for Increasing Transparency. PLoS Biology, 14(5), e1002456.
Kintigh, K. 
2006.	The Promise and Challenge of Archaeological Data Integration. American Antiquity, 71(3), 567-578.
Keers, G., van der Reijden, H., and H. van Rossum
2011.	Planning Archaeology: A Synthesis of the Thematic Sub-reports. RIGO Research en Advies, Amsterdam. 
Kratz J. and C. Strasser 
2015.	 Researcher Perspectives on Publication and Peer Review of Data. PLOS ONE 10(2): e0117619. DOI:10.1371/journal.pone.0117619, accessed 7 September 2017.
Kratz J. and C. Strasser 
2014.	Data publication consensus and controversies [version 1; referees: 1 approved with reservations]. F1000Research, Electronic document, https://f1000research.com/articles/3-94/v1, accessed 7 September 2017.
Kyzas P.A, K.T. Loizou, and J.P. Ioannidis
2005.	Selective reporting biases in cancer prognostic factor studies. Journal of the National Cancer Institute 97, 1043-1055.
Latour, B. 
1999.	Pandora's Hope: Essays on the Reality of Science Studies. Harvard University Press, Massachusetts. 
Leonelli, S. 
2016.	The Philosophy of Data, In The Routledge Handbook of Philosophy of Information, edited by L. Floridi. Routledge, New York.
Leonelli, S. 
2015.	 What Counts as Scientific Data? A Relational Framework. Philosophy of Science, 82(5), 810-821.
Marwick, B. 
2017.	Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of their Implementation. Journal of Archaeological Method and Theory, 24(2), 424-450.
Marwick, B., E. Hayes, C. Clarkson and R. Fullagar
2017.	Movement of Lithics by Trampling: An Experiment in the Madjedbebe Sediments, Northern Australia. Journal of Archaeological Science 79:73-85.
McCoy, M. D. and M. C. Codlin
2016.	The Influence of Religious Authority in Everyday Life: A Landscape-Scale Study of Domestic Architecture and Religious Law in Ancient Hawai’i. World Archaeology 48 (3):411–30.
McCullough B. D., K.A. McGeary and T. D. Harrison 
2006.	Lessons from the JMCB Archive. Journal of Money, Credit, and Banking 38(4), 1093-1107.
McCullough B. D. and H. D. Vinod
2005.	Comment: Econometrics and Software. Journal of Economic Perspectives 17(1), 223-224.
McMurry, J. A., Juty, N., Blomberg, N., Burdett, T., Conlin, T., Conte, N., Parkinson, H., Winfree, L., Mungall, C., Haendel, M. and H. Parkinson 
2017.	Identifiers for the 21st Century: How to Design, Provision, and Reuse Persistent Identifiers to Maximize Utility and Impact of Life Science Data. PLOS Biology, 15(6), e2001414. DOI:10.1371/journal.pbio.2001414, accessed on 7 September 2017.
Merton, R.K. 
1942.	The Normative Structure of Science. In The Sociology of Science: Theoretical and Empirical Investigations, edited by R. K. Merton, University Of Chicago Press, Chicago, Illinois. 
Moore, R., and J. Richards
2015.	Here Today, Gone Tomorrow: Open Access, Open Data and Digital Preservation. In Open Source Archaeology: Ethics and Practice, edited by Andrew T. Wilson, Ben Edwards, De Gruyter, Netherlands
Mounce, R. 
2014.	Open Data and Palaeontology. In Issues in Open Research Data, edited by S. A. Moore. pp. 151–164. Ubiquity Press, London.
National Science Foundation
2016.	Dissemination and Sharing of Research Results. Electronic document, https://www.nsf.gov/bfa/dias/policy/dmp.jsp, accessed 7 September 2017
Nicholas, G. P.
2014.	Indigenous cultural heritage in the age of technological reproducibility: Towards a postcolonial ethic of the public domain. In Dynamic Fair Dealing: Creating Canadian Culture Online, edited by Coombe, R. J., Wershler, D., and M. Zeilinger, pp. 213-24. University of Toronto Press, Toronto. 
Nicholas, G. P., and A. Wylie
2012.	Do Not Do Unto Others…’: Cultural misrecognition and the harms of appropriation in an open-source world. In Appropriating the Past: Philosophical Perspectives on Archaeological Practice, edited by R. Coningham and G. Scarre, pp. 195-221, Cambridge University Press, Cambridge.
Nicholas, G. P. and A. Wylie
2009.	Archaeological Finds: Legacies of Appropriation, Modes of Response. The Ethics of Cultural Appropriation, edited by J. O. Young and C. G. Brunk, pp. 11-54, Wiley-Blackwell, Oxford.
Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J. and T.  Yarkoni
2015.	Promoting an Open Research Culture: Author Guidelines for Journals Could Help to Promote Transparency, Openness, and Reproducibility. Science, 348, 1422–5.
Nugent, R., & Williams, H. 
2012.	Sighted surfaces: ocular agency in early Anglo-Saxon cremation burials. In Encountering Imagery: Materialities, Perceptions, Relations, edited by I.-M. Back Danielsson, F. Fahlander and Y. Sjöstrand. pp. 187-208, Stockholm University, Stockholm.
Nuijten, M. B., Borghuis, J., Veldkamp, C. L. S., Alvarez, L. D., van Assen, M. A. L. M., and J. M. Wicherts
2017.	Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psychology. Electronic document, https://psyarxiv.com/sgbta, accessed 7 September 2017
National Science Foundation
2010.	Data Management & Sharing Frequently Asked Questions (FAQs). Electronic document, https://www.nsf.gov/bfa/dias/policy/dmpfaqs.jsp#1, accessed on 7 September 2017
Pampel, H., Vierkant, P., Scholze, F., Bertelmann, R., Kindling, M., Klump, J. and U. Dierolf
2013	Making research data repositories visible: The re3data.org registry. PloS ONE, 8(11), e78080, DOI: 10.1371/journal.pone.0078080, accessed 7 September 2017.
Pavlech, L. L.
2016	 Data Citation Index. Journal of the Medical Library Association, 104(1), 88–90.
